From Questions to Queries – Enhancing the Curt System by a Theory and Implementation of Embedded WH-Questions

### 2008-08-30 thesis/paper.tex
wrote intro

>>>>

As access to vast amounts of information becomes more and more ubiquitous, and
the information accessible to humans grows more diverse every day, users
struggle to find what they need among the vast amounts of data. Current
search technologies aim to provide easy access to a constantly changing pool of
knowledge, yet they are hardly beyond the stage of looking for exact text
matches. Machine processing still fails to \emph{understand} the information it
has to deal with and sees data as nothing more than a set of strings. But often
a user's demands do not ask for a piece of text, but for an abstract concept, or
a relation. Knowing that natural language is most likely infinite, such
relations are virtually endless in number, and  one can only
conclude that trying to enumerate all human knowledge in gargantuan databases is
bound to be a never-ending task.
